### 2022-05-18 draft/draft.Rmd
minor changes based on meeting

### Likelihood Maximization Approaches to Block Models

@@

## Connecting the Stochastic Block Model and the Degree Corrected Block Model to the Generalized Random Dot Product Graph

>>>>

### Review of Likelihood Maximization Approaches to Block Models

@@

## Definitions

## Connecting the Stochastic Block Model to the Generalized Random Dot Product Graph

## Connecting the Degree Corrected Block Model to the Generalized Random Dot Product Graph

### 2022-05-18 draft/draft.tex
minor changes based on meeting

\newcommand{\diag}{\text{diag}}
\newcommand{\tr}{\text{Tr}}
\newcommand{\blockdiag}{\text{blockdiag}}
\newcommand{\indep}{\stackrel{\text{ind}}{\sim}}
\newcommand{\iid}{\stackrel{\text{iid}}{\sim}}
\newcommand{\Bernoulli}{\text{Bernoulli}}
\newcommand{\Betadist}{\text{Beta}}
\newcommand{\BG}{\text{BernoulliGraph}}
\newcommand{\Cat}{\text{Categorical}}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\theoremstyle{example}
\newtheorem*{example}{Example}

@@

Within the scope of this dissertation, we focus primarily on unweighted
and undirected graphs without self-loops. The adjacency matrix that
describes such a graph is binary, symmetric, and hollow. In this
setting, a plausible model is to sample each edge independently from a
Bernoulli distribution, i.e., \(A_{ij} \indep P_{ij}\) for some
\(P_{ij \in [0, 1]\) for each \(i < j\) (setting \(A_{ji} = A_{ij}\)
since \(A\) is symmetric, and \(A_{ii} = 0\) since \(A\) is hollow).
Then similar to how the edges are compiled into an adjacency matrix
\(A\), the edge probabilities can be compiled into an edge probability
matrix \(P \in [0, 1]^{n \times n}\). In order to provide structure

@@

\hypertarget{likelihood-maximization-approaches-to-block-models}{%
\subsubsection{Likelihood Maximization Approaches to Block
Models}\label{likelihood-maximization-approaches-to-block-models}}

@@

\hypertarget{connecting-the-stochastic-block-model-and-the-degree-corrected-block-model-to-the-generalized-random-dot-product-graph}{%
\subsection{Connecting the Stochastic Block Model and the Degree
Corrected Block Model to the Generalized Random Dot Product
Graph}\label{connecting-the-stochastic-block-model-and-the-degree-corrected-block-model-to-the-generalized-random-dot-product-graph}}

>>>>

\newcommand{\diag}{\mathrm{diag}}
\newcommand{\tr}{\mathrm{Tr}}
\newcommand{\blockdiag}{\mathrm{blockdiag}}
\newcommand{\indep}{\stackrel{\mathrm{ind}}{\sim}}
\newcommand{\iid}{\stackrel{\mathrm{iid}}{\sim}}
\newcommand{\Bernoulli}{\mathrm{Bernoulli}}
\newcommand{\Betadist}{\mathrm{Beta}}
\newcommand{\BG}{\mathrm{BernoulliGraph}}
\newcommand{\Uniform}{\mathrm{Uniform}}
\newcommand{\PABM}{\mathrm{PABM}}
\newcommand{\RDPG}{\mathrm{RDPG}}
\newcommand{\GRDPG}{\mathrm{GRDPG}}
\newcommand{\Multinomial}{\mathrm{Multinomial}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\as}{\stackrel{\mathrm{a.s.}}{\to}}
\newcommand{\ER}{\text{Erd\"{o}s-R\'{e}nyi}}

@@

Within the scope of this dissertation, we focus primarily on unweighted
and undirected graphs without self-loops. The adjacency matrix that
describes such a graph is binary, symmetric, and hollow. In this
setting, a plausible model is to sample each edge independently from a
Bernoulli distribution, i.e., \(A_{ij} \indep P_{ij}\) for some
\(P_{ij} \in [0, 1]\) for each \(i < j\) (setting \(A_{ji} = A_{ij}\)
since \(A\) is symmetric, and \(A_{ii} = 0\) since \(A\) is hollow).
Then similar to how the edges are compiled into an adjacency matrix
\(A\), the edge probabilities can be compiled into an edge probability
matrix \(P \in [0, 1]^{n \times n}\). In order to provide structure

@@

\hypertarget{review-of-likelihood-maximization-approaches-to-block-models}{%
\subsubsection{Review of Likelihood Maximization Approaches to Block
Models}\label{review-of-likelihood-maximization-approaches-to-block-models}}

@@

\hypertarget{definitions}{%
\subsection{Definitions}\label{definitions}}

\hypertarget{connecting-the-stochastic-block-model-to-the-generalized-random-dot-product-graph}{%
\subsection{Connecting the Stochastic Block Model to the Generalized
Random Dot Product
Graph}\label{connecting-the-stochastic-block-model-to-the-generalized-random-dot-product-graph}}

\hypertarget{connecting-the-degree-corrected-block-model-to-the-generalized-random-dot-product-graph}{%
\subsection{Connecting the Degree Corrected Block Model to the
Generalized Random Dot Product
Graph}\label{connecting-the-degree-corrected-block-model-to-the-generalized-random-dot-product-graph}}
